Quality assurance of digital twins -- An experience report in the automotive industry

### 2023-02-06 manuscripts/paper-1/main.tex
Second Part Finished

    \section{State of the art on quality}
    TODO

    \subsection{Product quality}
    Most generic (e.g.~House of quality, ...)

    \subsection{Software quality}
    Medium (e.g.~ISO/IEC 9126 and ISO 25010, ...)

    \subsection{Digital twin quality}
    Most specific (a bit more research here!)

@@

    \subsubsection{Definition}
    Effort to adapt the digital twin to new circumstances (e.g.\ add new machine, replace machine, etc.)

@@

    \begin{comment}
        \section{Whatever}

        \subsection{Grieves Information Mirroring Model}

        \subsubsection{How it is defined?}

        His conceptual model is an ideal Product Lifecycle Management (PLM), has just one important goal which is to gather as much information about the actual space as feasible to minimize the waste of energy, time, and materials. 
        It is composed primarily of four parts. Real or physical space, virtual space, connections between real and virtual space, and virtual simulations.

        As we can see, it shares almost all of the same components as the digital twins of today. Virtual simulation is an optional component that Grieves subsequently removed to simplify the model. [GrievesEliminateForthElement] 
        The simple model version is indicated by the fact that only the first three (Physical System, Virtual System, and Connection Between Them) will be taken into account. 
        It should be mentioned that we shall define these three components in our own words using previous definitions of each component.  Additionally, by using the consortium's definition, we are simply improving the grieves IM model as a reference.
        The physical space is where we start first.

        \begin{figure}[htbp]
            \includegraphics[width=\columnwidth]{Grieves Information Mirroring Model.png}
            \caption{Information Mirroring Model}
            \label{IM}
        \end{figure}

        \subsubsection{Why it is problematic?}

        TODO

        \subsection{Real System}
        We shall refer to a real system instead of calling it a real space. 
        Why? Because everything is an open system according to the system theory, 
        with the upper bound of the universe and lower bound as subatomic particles.
        As a result, the universe and subatomic particles can be viewed as closed systems, 
        simplifying definitions and facilitating the analysis of entities as systems. 
        In the literature, we see most of the time a notion called " entity" and sometimes an "artifact". 
        For instance, the digital twin framework developed by (TAO et al.) has both a physical and virtual entity.
        An entity is any separate and independent system, whether it be real or abstract.
        On the other hand, an artifact is a thing that humans have created or constructed. 
        Therefore, when we speak of entities, we really mean systems. 
        And when we discuss artifacts, we are still discussing physical systems but with the caveat of human interaction. 
        Automobiles, engines, software, artwork, food, and telephones are a few examples of artifacts.

        Above, we established the term "entity," but what about the physical connection of an entity? 
        Because an entity could be a physical system or an abstract system. 
        We won't go into further depth about these two distinct ideas, but just so you know, 
        when we talk about physical systems, we do not include abstract systems that require a
        media to exist, such as ideas, texts, diagrams, and mathematics, which are nothing more than abstractions.

        The term "real system" in the context of digital twins refers to a system that is a tangible thing and also has 
        the characteristics of a system. The usage of various artifacts by Grieves in a system he referred to as `real space' 
        can be seen in figure X. 
        For convenience, we'll refer to this system as a "real system" or, as Mobus prefers to say, a `system of interest.'. 
        Instead of using black-and-white images, we instead created subsystems out of circles, each of which represented an artifact. 
        It is clear to see that every subsystem (artifact) includes smaller subsystems as well. 
        Once more using Grieves' example, an automobile(an element of the real space according to figure 1), 
        which is an artifact, that includes several parts, including a radio, a motor, wheels, etc. 
        Additionally, these subsystems (artifacts) can be further broken down into even smaller subsystems, 
        down to subatomic particles, which, as we mentioned above, is the lowest we can go in terms of the system theory. 
        But the question is, should we break things down to the level of subatomic particles to comprehend the system? Considering digital twins, 
        the answer is a resounding no.

        Consequently, why bother to define these terms? Because the granularity of the digital twin is determined by the complexity of the real system. 
        In the end, a System of Interest is what we'll be twinning! Of course, the system of interest is not as simple to define as in figure X. 
        One crucial component and stage of the digital twin is to comprehend how the real system, or more precisely the system of interest, 
        actually functions. How can one know what to twin if it is not well understood?
        The system of interest can be analyzed in three different ways. If we don't have the opportunity to examine the inner workings of the system, 
        we can use the black boxing technique, which focuses primarily on the mathematical (and frequently statistical) 
        relationships between inputs and outputs. This method doesn't provide insight into the inner workings of the system, but it still provides 
        a basic grasp of how a system operates. If the system exhibits linear behavior, it works great.

        The second method, known as the gray box method, examines the inner workings of comparable systems that should be `like' 
        the system of interest to understand how the inner workings of a similar system react when various inputs are applied and the results of the system are monitored. 
        This method is used for the majority of biological work, such as the experiments medical students conduct on cadavers to learn how the human body functions.

        The final method, known as the `white box method,' is better than the others since it examines every system's component. 
        The interesting thing to realize is that the system's integrity(Objectiveness) shouldn't be impaired.
        What objectiveness means is that while the system functions as a whole, we should also study the relationships 
        between the subsystems in addition to the subsystems themselves. 
        Observing our galaxy is a fantastic example. Telescopes allow us to individually assess the condition of the subsystems (planets, solar systems) 
        without affecting the overall system.

        Physical space, as a whole, is a physical system (which we refer to as the system of interest),
        with subsystems and linkages between them. Depending on the SOI's context, we can use black box, gray box, or white box methodologies to study the system.
        In addition, I wish to draw attention to the fact that the SOI's details are not fully depicted in figure 2. 
        For additional details on the system theory, we strongly advise reading `von Bertalanffy 2003'.

        \begin{figure}[htbp]
            \includegraphics[width=\columnwidth]{SOI.png}
            \caption{System Of Interest}
            \label{SOI}
        \end{figure}

        \subsection{Virtual System(Digital Twin)}

        First of all, what does the term `virtual' mean? Virtual refers to an existence (or entity?) that exists in a computer system as opposed to a physical system. 
        Therefore, we made sure to note that we are not speaking of abstract systems when we described physical systems. 
        We also discussed the distinction between an entity and an artifact. The term `abstract systems'  refers to systems that have had their set of variables and functions 
        `abstracted'  so that they may be computed by a solver, which in this case could be either the human brain or a computer.
        Additionally, just because a system is abstract doesn't mean it lacks a physical body; rather, as we previously established, 
        it is abstracted. Computers, symbolic language, and the human mind all can contain these abstract systems.
        Symbolic text in this sense covers not only text on the sheet but also mathematical symbols, logic, etc.

        Virtual systems can't exist on their own since, like abstract systems, they require a medium to exist.
        Computer systems, a higher system of virtual systems, are an ideal medium for virtual systems.

        \begin{figure}[htbp]
            \includegraphics[width=\columnwidth]{DT SOI.png}
            \caption{Digital Twin SOI}
            \label{DTSOI}
        \end{figure}

        Recall that Grieves referred to the virtual system as a virtual space in figure 1. 
        We refer to it as a virtual system because it can only exist inside a computer system. 
        Additionally, we refer to the entities he depicted in the virtual space as virtual subsystems rather than the virtual entities he used. In figure 3, 
        we were creative and wrote `digital twin'  rather than `virtual system.'  Where does this digital twin emerge from?

        We must first understand what digital implies to comprehend the concept of a digital twin.  
        The term `digital has been in use since the late 14th century and is derived from the Latin word `digitus, ' 
        which means `finger'  or `toe.'. It gained popularity after digitalization in the 20th century and refers to the use of discrete digits to represent data. 
        Digital images, for instance, are represented by a matrix of pixels, which are nothing more than 8-bit integer values between 0 and 255 which represent the intensity 
        of the pixel. 
        We will therefore have digital models if we can digitally model our models. 
        Therefore, we will have digital models if we can digitally model our models. Where are these digital models being created? Throughout the digital system! 
        This system is referred to as a `digital twin'  since it is a digital twin of the SOI that is represented in the computer system.

        The reader will quickly and easily comprehend that a computer system may have several digital twins, 
        and that these systems may also be connected in some way, 
        creating yet another system that is also referred to as a digital twin. 
        Another immediate realization is that perhaps we won't have our SOI yet, 
        so how can we twin something that doesn't exist? Although the term we preferred was the best definition (for us), 
        it does not directly address the second question. In reality, most of the time, 
        the physical product will not be ready or not present to make a digital twin out of it. 
        But if we could have some data about the physical system, for example how it should look, 
        how much weight it should have, approximate dimensions and so on,  we can start constructing our system abstractly, 
        within the computer systems, with diagrams, or with using symbolic language. 
        But the important point is that everyone, who works on this abstract system should have a singular reference so that it can be constructed. Also after the construction, 
        still a real system is needed to validate and verify. Most frequently, this viewpoint is referred to as a prototype digital twin. And if the SOI is present its called instance digital twin.

        So far, we inspected the real system (system of interest), and virtual system. 
        As we talked about above, there is a third part which is a connection between the real system and the virtual system, which we will explain next.

        \subsection{Connection Between the Systems}

        \subsection{Possibility of States}
        \subsection{Context of Digital Twin}
        \subsection{Quality of Digital Twin}
    \end{comment}

    \begin{comment}
        \section{Literature review}
        \label{section: literature}
        Literature analysis was executed, to analyze current DT literature within the concept of digital twin quality. The analysis especially focused on 
        how the digital twin quality is mentioned and assessed within the academic dissertations.

        Methodology (see Section~\ref{section:liteature_methodology}), Result (see Section~\ref{section:liteature_result}), and Summary (See Section~\ref{section:liteature_summary})...

        \subsection{Methodology}
        \label{section:liteature_methodology}
        Google Scholar (GS), Scopus (SCP) and Research Rabbit (RR) tools are used to fulfill our requirements for the literature review. 
        Since there is a great number of digital twin publications in academics, 
        narrowing the research is necessary, so the following algorithm which can be seen in Figure \ref{fig:literaturesearchalgorithm} with several levels of filtering will be applied.

        First filtering will be done with the following criteria:
        \begin{itemize}
            \item Dissertations should be written in English and published in a journal/conference.
            \item Dissertations should not be older than 2018
            \item Search term should be exactly searched.
        \end{itemize}

        Filtering query calls for the GS and SCP are the following:
        \begin{itemize}
            \item Google Scholar = "search term"
            \item Scopus = ALL ( "digital twin quality" ) AND PUBYEAR > 2018 AND PUBYEAR < 2023 AND ( LIMIT-TO (LANGUAGE , "English" )) 
        \end{itemize}

        Also want to note that, in the GS, there isn't a function that filters the dates, instead the user should click the Since 2018 option to filter the dates.

        If an interesting dissertation(s) would be found during the reading, it will be checked again with the first filter.
        \begin{figure}
            \centering
            \includegraphics[width =0.45\textwidth]{LRMethod.png}
            \caption{Literature Search Algorithm}
            \label{fig:literaturesearchalgorithm}
        \end{figure} 
        \begin{figure}
            \centering
            \includegraphics[width =0.45\textwidth]{LRMethodLegacy.png}
            \caption{Literature Search Algorithm Legend}
            \label{fig:literaturesearchalgorithmlegend}
        \end{figure}

        \subsection{Result}
        \label{section:liteature_result}
        The following results were achieved by selecting several search terms.

        \subsubsection*{Digital Twin Quality}
        \label{subsection:DigitalTwinQuality}
        First filtering was done for the search term "digital twin quality", meanwhile GS gave 41 different results, and SCP gave only 3 results.
        After the second filtering process, 3 duplications and 31 different results were found. 10 dissertations were not in English.
        After the third filtering process, 9 dissertations passed and the rest is rejected.

        \subsubsection*{Digital Twin Model Verification}
        \label{subsection:DigitalTwinVerification}

        \subsubsection*{Digital Twin Model Validation}
        \label{subsection:DigitalTwinValidation}
        %What is the existing literature?

        \subsection{Summary}~\label{section:liteature_summary}
        What do we learn from existing literature?

        He Zhang et al.introduced a consistency evaluation method for digital twin models, which can be used to assess the quality of the digital twin ~\cite{Jones2020}.
        (Existing literature does at most partially solve our problem!)
    \end{comment}

@@

    \begin{comment}
        \section{Case study (FELICE)}\label{section:case}
        TODO (Explain the limitations of the FELICE digital twin! It is not a complete digital twin according to literature! It includes this, it is missing this.)

        \subsection{Methodology}~\label{section:case_methodology}
        TODO

        \subsection{Result}~\label{section:case_result}
        TODO

        \subsection{Summary}~\label{section:case_summary}
        TODO
    \end{comment}

>>>>

    \section{State of the art on quality}
    In the Oxford English Dictionary, the word `quality' is described as a noun as well as an adjective. The Adjective form indicates, a high standard or excellence. 
    For example, the phrase `quality products' implies that quality adds a high standard state to the product. 
    There are several meanings for the noun, but the one that interests us in this situation is `the standard of something as measured against other things of a similar kind. \cite{OxfordDictionary}'
    This definition shows the relativity of quality.

    According to ISO 9000:2015, quality is the degree to which a set of inherent characteristics of an object fulfills requirements~\cite{ISO9000}. Several words need to be expanded, to understand this definition.

    First, the standard also explains characteristics as distinguishing features such as physical, sensory, behavioral, temporal, ergonomic and functional. 
    Instead of an object, a system can be used for more generalization.
    As for the requirements, the standard also explains as a requirement is a need or expectation that is stated, generally implied or obligatory.~\cite{ISO9000}

    Thus, when these definitions are combined, we obtain the following: `Quality is a degree to which a set of inherent distinguishing features of a system fulfills a need or expectation that is stated, generally implied or obligatory'. 
    It should be highlighted that there are various quality definitions by so-called `Quality Gurus', but the authors decided to expand the standard definition of ISO 9000.

    \subsection{Product quality and Management}
    A product is a tangible or intangible system that satisfies the needs or wants of a customer. It could be a physical system like a car, or an abstract system, like a digital twin. 
    Regarding product quality, there are two different aspects~\cite{GrievesPLMBook}.
    First, quality is an attribute of a product, which meets product specifications. Specifications are mostly defined by the supra-systems subsystems, such as by the stakeholders within the supra-system,  If the stakeholders' expectations, or needs, are met, we can consider high quality.
    The ability to execute to a specific usage standard is the second facet of product quality. Since this standardization is usually not controllable, unlike the first, the system's quality will be determined by how the implied or obligatory standards are fulfilled.

    Quality management is a management type, which has an interest in Quality, and quality assurance is one of the parts of quality management, 
    which focuses on providing fidelity that quality requirements will be fulfilled. This means that quality assurance is a subsystem of quality management.

    Quality management systems(QMS) are being used to plan and execute the organization's quality policies and goals. 
    Examples of such systems can be a standard like ISO 9001 which can provide a framework for an organization, or a data-driven methodology 
    such as Six Sigma to reduce defects and improve efficiency. These concepts are not new, for example, ISO 9001 standard has been established in 1987, 
    and is still being regularly updated~\cite{ISO9001DebunkingtheMyth}.

    \subsection{Software quality}
    Software is a  virtual system, which has a set of instructions, data or programs used to perform a specific task. 
    All virtual systems, which we described above, need a medium to live on, hence these systems can be found in a computer or other electronic device.  
    Software quality according to IEEE 730-2014, is: 
    `The degree to which a software product meets established requirements; however, 
    quality depends upon the degree to which those established requirements accurately represent stakeholder needs, wants, and expectations'~\cite{IEE730-2014}. 
    As can be seen, it's a generic explanation of a quality, which doesn't differ much from the explanation we gave above.

    Software quality management techniques come from already used manufacturing techniques in the industries.
    For example, the quality assurance which we mentioned above, also has been used as a software quality management activity with some differences. 
    In manufacturing, products will never exactly meet a specification, due to errors in the machining so there should be some tolerance for the manufacturing. 
    But in the software systems, or more precisely in the virtual systems, it's most of the time, not the case. 
    Also its nearly impossible to conclude that, the software product fully meets its specifications\cite{SoftwareEngineering}.

    According to ISO/IEC:25010:2011, there are eight software quality attributes. Functional Suitability, 
    Performance efficiency, compatibility, usability, reliability, security, maintainability and portability.\cite{ISO/IEC:25010}
    Of course, not all aspects can be inspected and the person, who is responsible for the quality of the product, should choose the critical aspects of the software product and further the process according to that decision.

    \subsection{Digital twin quality}
    To analyze current DT literature within the concept of digital twin quality literature analysis was executed. 
    The analysis especially focused on how the digital twin quality is mentioned and assessed within the academic dissertations.

    \subsubsection*{Literature Search Methodology}
    Google Scholar (GS), Scopus (SCP) and Research Rabbit (RR) tools are used to fulfill our requirements for the literature review. Since there is a great number of digital twin publications in academics,
    narrowing the research is necessary, so the following algorithm with several levels of filtering will be applied.

    First filtering will be done with the following criteria

    \begin{itemize}
        \item  Dissertations should be written in English and published in a journal/conference.
        \item  Dissertations should not be older than 2016
        \item  Search term should be exactly searched
    \end{itemize}

    Filtering query calls for the GS and SCP are the following
    \begin{itemize}
        \item Google Scholar = `search term'
        \item Scopus = ALL (`digital twin quality') AND PUBYEAR > 2016 AND PUBYEAR < 2023 AND (LIMIT-TO (LANGUAGE, `English'))
    \end{itemize}
    Also want to note that, in the GS, there isn't a function that filters the dates, instead the user should click the Since 2016 option to filter the dates.

    If an interesting dissertation(s) would be found during the reading, it will be checked again with the first filter.

    \subsection*{Literature Result}
    First filtering was done for the search term "digital twin quality", meanwhile GS gave 41 different results, and SCP gave only 3 results. After the second filtering process, 3 duplications and 31 different results were found and 10 dissertations were not in English. 
    After the third filtering process, 9 dissertations passed and the rest is rejected.

    \subsection*{Important Findings}

    Important findings are the following;

    \begin{itemize}
        \item Shcherba et al. center their attention on the model quality, which is an observation for a digital twin subsystem. Despite being a crucial component of the digital twin, models alone cannot be used to assess the quality of the digital twin.
        \item A consistency evaluation approach for digital twin models was developed by He Zhang et al. and can be used to assess the quality of the models. Additionally, the authors discuss crucial ideas like consistency between real and virtual systems and ultra-fidelity models. The improvement of the service component is the primary emphasis of this article. Tao's five-dimensional digital twin concept includes this component.
        \item He Zhang et al. introduce the updating method for digital twin models in yet another insightful article. Once more, the accuracy and coherence of the model concepts were addressed.
        \item Selch et al. work is the only one that discusses the quality of the digital twin. The paper presents a machine-learning approach based on Bayesian networks to track the quality of the digital twin. The unique aspect of this study is that the author, rather than just analyzing the digital twin as a single system, determines the contributions of subsystems to forecast the overall quality of the digital twin. The digital couplings, which are linkages between the subsystems, are also mentioned by Selch et al. as a source of extra uncertainty. 
        Since only one digital twin has been used in practice, multiple subsystem digital twins have not been validated.
    \end{itemize}

@@

    \subsubsection{Definition}
    Efforts to adapt the digital twin to new circumstances (e.g.\ add a new machine, replace the machine, etc.)

@@

@@
